A Simple Minibatch Acceptance Test for MCMC

### 2016-05-17 nips_2016.tex
still writing exp

\begin{algorithm}[t]
\KwData{this text}
\KwResult{how to write algorithm with \LaTeX2e } initialization\;
\While{not at end of this document}{
    read current\;
    \eIf{understand}{
        go to next section\;
        current section becomes this one\;
    }{
        go back to the beginning of current section\;
    }
}
\caption{A description of our MH test.}
\label{alg:our_algorithm}
\end{algorithm}

@@

\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will be a sequence of images for logistic regression.}
\end{figure}

@@

\subsection{Neural Network Optimization}\label{ssec:nets}
In this experiment, we apply about mini-batch MH testing with SGHMC proposer to sample the parameter instances from a fully connected neural network.
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}

>>>>

\begin{algorithm}[t]
\KwData{$\{x_i\}$ under a target distribution}
\KwResult{a serise of sampled $\{\theta_i\}$ under the posterior distribution} 
set the $var(\Delta') = 1.0$ and deconvolve $X$ to get the disribution of $X_{corr}$\;
\While{not enough sampled data}{
	estimate the $sd(\Delta')$\;
    propose a candidate $\theta'$\;
    compute the noisy $\Delta'$\;
    sample a $x$ from $X_{corr}$;
    \eIf{$x*sd(\Delta') + \Delta' > 0$}{
        accpet the $\theta'$;
    }{
        reject the $\theta'$;
    }
}
\caption{A description of our MH test.}
\label{alg:our_algorithm}
\end{algorithm}

@@

@@

\subsection{Neural Network Optimization}\label{ssec:nets}
In this experiment, we apply about mini-batch MH testing with SGHMC proposer to sample the parameter instances from a fully connected neural network. We use Higgs data set from University of California Irvine. It is a classification problem to distinguish between a signal process which produces Higgs bosons and a background process which does not. We build a 4 layers neural network to tackle this problem. The first layer is a input layer, the last layer is a softmax layer, the intermediate layers are linear followed by Sigmoid, norm, dropout, starting and ending with linear operation.

We choose the 
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}
